---
title: "Inferential Statistics - Course Project part 2"
author: "Maurizio Murino"
date: "29 January 2016"
output: html_document
---

## Introduction

Now in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package.

## Data load, exploration ans summary
_Points 1 and 2._

``` {r}
"datasets" %in% row.names(installed.packages())
library(datasets)
data("ToothGrowth")
dim(ToothGrowth)
class(ToothGrowth)
str(ToothGrowth)
summary(ToothGrowth)
```

We got a 60 rows dataset for three variables: "Tooth length", "Supplement lenght", "Dose in milligrams per day".

```{r}
with(ToothGrowth, coplot(len ~ dose | supp))
```

The plot shows the response in the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

## Confidence inyervals/hypothesis tests.
_Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)._

Vitamin C delivery methods affect the tooth length of the guinea pigs?
H0: true difference in means is equal to zero.

### t-test

```{r}
with(ToothGrowth, t.test(len[supp=="OJ"], len[supp=="VC"], paired = FALSE, var.equal = FALSE))
```

P-value of this test is 0.06. It could be interpreted as a lack of evidence to reject the null hypothesis. We cannot assume that the vitamin delivery method affect the tooth length.

Same t test for the tooth length of the group with vitamin C dosage.